### 2021-12-06 input/proposal.tex
almost nothing here

\begin{proof}
  % When there are no sources, no \process receives, nor delivers hence
  % forwards any message. \Processes do not belong to any partition.
  \noindent \TODO{use total order ($<$) and sets $R_p D_p$} Whenever a
  \process $s$ becomes a source, it delivers its own message
  $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever its set of received
  messages, its own partition $P_s$ becomes and remains its closest
  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq
  s: |\Pi_{s s}| < |\Pi_{s x}|$.
  %
  \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
  Since communication links are reliable, neighboring \processes
  eventually receive such a notification
  $\forall \langle s, y \rangle \in E \iff \eventually
  r_y(\alpha_{s}^{d})$. Most importantly, whatever the order of
  received messages, every \process $q$ in this neighborhood such that
  there exists no closer source $s'$ than the received one $s$,
  delivers it, since $w_{sq} < |\Pi_{s'q}|$.
  %
  \noindent They forward it and their respective neighbors eventually
  receive it. By transitivity, the message originating from $s$
  reaches all \processes belonging to $P_s$ at least through their
  shortest paths: $\smash{\forall q' \in V, s, s' \in S: |\Pi_{s q'}| <
  |\Pi_{s' q'}| \implies \eventually d_{q'}(\alpha_{s}^{|\Pi_{sq'}|})}$.
  Since there exists only one best sum of weights per \process that
  can never be retracted, \processes eventually reach consistent
  partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}

>>>>

\begin{proof}
  % When there are no sources, no \process receives, nor delivers hence
  % forwards any message. \Processes do not belong to any partition.
  % \noindent \TODO{use total order ($<$) and sets $R_p D_p$}
  Whenever a \process $s$ becomes a source, it delivers its own
  message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever its set of received
  messages, its own partition $P_s$ becomes and remains its closest
  partition $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ since $|\pi_{ss}|$ is
  its greatest lower bound.
  %
  \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
  Since communication links are reliable, neighboring \processes
  eventually receive such a notification
  $\forall \langle s, y \rangle \in E \iff \eventually
  r_y(\alpha_{s}^{d})$. Most importantly, whatever the order of
  received messages, every \process $q$ in this neighborhood such that
  there exists no closer source $s'$ than the received one $s$,
  delivers it, since $w_{sq} < |\Pi_{s'q}|$.
  %
  \noindent They forward it and their respective neighbors eventually
  receive it. By transitivity, the message originating from $s$
  reaches all \processes belonging to $P_s$ at least through their
  shortest paths: $\smash{\forall q' \in V, s, s' \in S: |\Pi_{s q'}| <
  |\Pi_{s' q'}| \implies \eventually d_{q'}(\alpha_{s}^{|\Pi_{sq'}|})}$.
  Since there exists only one best sum of weights per \process that
  can never be retracted, \processes eventually reach consistent
  partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}
